### 2024-02-22 supporting.tex
Added number and percentage of regions passing the rate cutoffs to hierarchy_histogram caption

\begin{figure}[h!]
\includegraphics[width=\textwidth]{hierarchy/out/hierarchy_histogram.png}
\centering
\caption{\textbf{Rate distributions of substitution models fit to disorder regions.}
\textbf{(A)} Average amino acid rates in regions.
\textbf{(B)}. Average indel rates in regions. For both panels, the grey intervals correspond to the subset of rapidly evolving regions used for the clustering and GO term enrichment analyses.}
\label{sfig:hierarchy_histogram}
\end{figure}

>>>>

\begin{figure}[h!]
\includegraphics[width=\textwidth]{hierarchy/out/hierarchy_histogram.png}
\centering
\caption{\textbf{Rate distributions of substitution models fit to disorder regions.}
\textbf{(A)} Average amino acid rates in regions.
\textbf{(B)} Average indel rates in regions. For both panels, the grey intervals correspond to the subsets of rapidly evolving regions used for the clustering and GO term enrichment analyses. 5892 (52\%) and 6052 (53\%) regions pass the amino acid and indel rate cutoffs, respectively, and 7607 (67\%) of regions pass either.}
\label{sfig:hierarchy_histogram}
\end{figure}
